Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-27 article.tex
introduction of appendix

@@

\subsection*{Signal processing}

@@

Besides filters $f_1$ and $f_2$ respectively defined by equations \ref{eq
:symetric-median} and \ref{eq:weighted-asymetric-median}, we also consider two
other low-pass filters
\begin{align}
f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i, \label{eq:asymetric-median-forward} \\
f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i. \label{eq:asymetric-median}
\end{align}

@@

After the hard thresholded filter $h$, they were significant differences in
peak magnitudes. Since timeseries $x_i^t$  were mainly between 0 and 1,
we smoothened these differences in peak magnitudes through
\begin{align}
g(x^t_i) = (x_i^t)^c
\end{align}
yielding slightly better AUROC with $c=0.9 \in (0, 1)$.

@@

\subsection*{Averaging the connectome inference from partial correlation statistics}

@@

\subsection*{Connectome inference from pairwise interaction statistics}

Since partial correlation statistics is a symmetric measure and the connectome
is a directed graph, it should be rewarding to detect the edge orientation. In
this section, we will present a heuristic trying to retrieve directivity.
However, considering results in Section \ref{sec:results}, we expect that the
additional gain margin should be extremely limited.

@@

>>>>

This appendix is structured as follows: Section \ref{app:signal} describes the differences about the signal processing methods applied on fluorescent calcium time series; Section \ref{app:averaging} then provides a detailed explanation of the averaging approach; Section \ref{app:connectome} presents a heuristic trying to retrieve directivity from fluorescent calcium time series while Section \ref{app:results} finally present results validating some choices that have been made.

%% plan

@@

\subsection{Signal processing}
\ref{sapp:signal}

@@

Besides filters $f_1$ and $f_2$ respectively defined by equations \ref{eq:symetric-median} 
and \ref{eq:weighted-asymetric-median}, we also consider two
other low-pass filters
\begin{align}
f_3(x^t_i) &= x^{t-1}_i + x^{t}_i + x^{t+1}_i + x^{t+2}_i, \label{eq:asymetric-median-forward} \\
f_4(x^t_i) &=  x_i^t + x^{t+1}_i  + x^{t+2}_i + x^{t+3}_i. \label{eq:asymetric-median}
\end{align}

@@

After the hard thresholded filter $h$, they were significant differences in
peak magnitudes. Since timeseries $x_i^t$  were mainly between 0 and 1,
we smoothened the difference in peak magnitudes through
\begin{align}
g(x^t_i) = (x_i^t)^c
\end{align}
yield slightly AUROC with $c=0.9 \in (0, 1)$.

@@

\subsection{Averaging the connectome inference from partial correlation statistics}
\ref{sapp:averaging}

%% plus en évidence le weighted - tenant compte des performances

@@

\subsection{Connectome inference from pairwise interaction statistics}
\ref{sapp:connectome}

Since partial correlation statistics is a symmetric measure and the connectome
is a directed graph, it should be rewarding to detect the edge orientation. In
this section, we will present a heuristic trying to retrieve directivity.
However, considering results in Section \ref{sec:results}, we expect that the
additionnal gain margin should be extremely limited.

@@

\subsection{Experiments}
\ref{sapp:results}
